---
title: "Identification of the odd positive integers and prime numbers using a square wave version of Riemann Zeta generating function"
author: "John P. D. Martin"
date: "January 29, 2017"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Executive Summary

Using a modified version of the Riemann Zeta generating function (based on the extended Riemann Siegel functional form) produces a square wave version of the Riemann Zeta function along the positive real axis. This function can be used to highlight and identify the positive odd integers and prime numbers.


##Introduction

The Riemann Zeta function is defined (1), in the complex plane by the integral 

\begin{equation}
\zeta(s) = \frac{\prod(-s)}{2\pi i}\int_{C_{\epsilon,\delta}} \frac{(-x)^s}{(e^{x}-1)x}dx
\end{equation}


where $s \thinspace \epsilon \thinspace \mathbb{C}$ and $C_{\epsilon,\delta}$ is the contour about the imaginary poles.

The Riemann Zeta function has been shown to obey the functional equation (2)

\begin{equation}
\zeta(s) = \zeta(1-s)*(2^s\pi^{s-1}sin(\frac{\pi s}{2})\Gamma(1-s)) \label{eq:func}
\end{equation}

Following directly from the form of the functional equation and the properties of the coefficients on the RHS of eqn \eqref{eq:func} it has been shown that any zeroes off the critical line would be paired, ie. if $\zeta(s)$ = 0 was true then $\zeta(1-s) = 0$.

The Riemann Siegel function is an exact function (3) for the magnitude of the Riemann Zeta function along the critical line (0.5+it) of the form

\begin{equation}
Z(t) = \zeta(0.5+it)e^{i\theta(t)} \label{eq:rs}
\end{equation}

where 

\begin{equation}
\theta(t) = \Im(ln(\Gamma(\frac{1}{4}+\frac{1}{2}it)))-\frac{t}{2}ln(\pi) \label{eq:theta}
\end{equation}

In Martin (4) and earlier work, the properties of the Riemann Zeta generating function were investigated and used to define and investigate the extended Riemann Siegel $Z_{ext}(s)$ and $\theta_{ext}(s)$ functions away from the critical line. 

\begin{align}
e^{i\theta_{ext}(s)} &= \sqrt{\frac{\zeta(1-s)abs(2^s\pi^{s-1}sin(\frac{\pi s}{2})\Gamma(1-s))}{\zeta(s)}}  \label{eq:exptheta} \\ \theta_{ext}(s) &= \Im(log(e^{i*\theta_{ext}(s)})) \\
\\ &= \Im(log(\sqrt{\frac{\zeta(1-s)abs(2^s\pi^{s-1}sin(\frac{\pi s}{2})\Gamma(1-s))}{\zeta(s)}}))  
\end{align}

\begin{align}
Z_{ext}(s) &= \sqrt{\zeta(s)*\zeta(1-s)*abs(2^s\pi^{s-1}sin(\frac{\pi s}{2})\Gamma(1-s))} \label{eq:zext}
\end{align}

where consistent with eqn \eqref{eq:rs}

\begin{align}
\zeta(s) &= Z_{ext}(s)*e^{-i\theta_{ext}(s)} 
\end{align}

In particular, only on the critical line s=(0.5+i*t) is the cancellation exact between the coupled, extended Riemann Siegel functions eqns \eqref{eq:exptheta} and \eqref{eq:zext}, resulting in Riemann Zeta zeroes. 

In this paper from eqns \eqref{eq:exptheta}-\eqref{eq:zext}, 

\begin{align}
\frac{Z_{ext}(s)^2}{\zeta(s)} &= Z_{ext}(s)*e^{+i\theta_{ext}(s)}
\end{align}

is used to create a square wave Riemann Zeta generating function, which highlights and identifies the odd positive integers and prime numbers. 

##Square wave version of Riemann Zeta generating function

Using eqn eqns \eqref{eq:exptheta}-\eqref{eq:zext} it can be shown that

\begin{align}
\frac{Z_{ext}(s)^2}{\zeta(s)} = Z_{ext}(s)*e^{+i\theta_{ext}(s)} &= \zeta(1-s)*abs(2^s\pi^{s-1}sin(\frac{\pi s}{2})\Gamma(1-s)) \label{eq:zetasq}
\end{align}

which is almost the Riemann Zeta generating function eqn \eqref{eq:func} except for the use of the absolute value for the second term in eqn \eqref{eq:zetasq}.

As shown in figure 1, the waveform generated is asymptotically a square wave, along the positive x axis since $\zeta(s)$ rapidly tends to 1 on that line. 


```{r, square, echo=FALSE, cache=TRUE, fig.width=6, fig.height=5,  fig.keep='high', warning=FALSE }
# [42] The LMFDB Collaboration, 
# The L-functions and Modular Forms Database, 
# Home page → L-functions → Zeros of ζ(s)
# http://www.lmfdb.org/zeros/zeta/?limit=100000&t=14.134725141734695 [Online; accessed 22 October 2016].

library(pracma)

# lis_z <- read.csv("/home/john/Downloads/zeroes_16000.tsv",sep=" ")
lis_z <- read.csv("/home/john/Downloads/zeroes_100000.tsv",sep=" ")

fratio <- function(res,x) {
  (2^(res+1i*x)*pi^(res+1i*x-1)*sin(pi/2*(res+1i*x))*gammaz(1-(res+1i*x)))
}

rawratio <- function(res,x) {
  abs(2^(res+1i*x)*pi^(res+1i*x-1)*sin(pi/2*(res+1i*x))*gammaz(1-(res+1i*x)))
}

otherfn <- function(res,x) {
  0.5*(res+1i*x)*(res+1i*x-1)*pi^(-(res+1i*x)/2)*gammaz((res+1i*x)/2)
}

otherfn2 <- function(res,x) {
  pi^(-(res+1i*x)/2)*(res+1i*x-1)*gammaz((res+1i*x)/2+1)
}


theta <- function(res,x) {
  sqrt(zeta(1-(res+1i*x))*rawratio(res,x)/zeta(res+1i*x))
}

zed <- function(res,x) {
  sqrt(zeta(1-(res+1i*x))*rawratio(res,x)*zeta(res+1i*x))
}

rawratio_fn <- function(x) {
  rawratio(res,x)
}

der_rawratio_fn <- function(x) {fderiv(rawratio_fn,x,1)}

zeta_fn <- function(x) {
  zeta(x)
}


der_zeta_fn <- function(x) {fderiv(zeta_fn,x,1)}

gamma_fn <- function(x) {
  gammaz(x)
}

der_gamma_fn <- function(x) {fderiv(gamma_fn,x,1)}

bern_fn <- function(x) {
  -1*zeta(1-x)*(2*pi)^(x)/2/gammaz(x)
}

der_bern_fn <- function(x) {fderiv(bern_fn,x,1)}

dzeta_fn <- function(x) {
  Re(zeta(x)/exp(pi*1i*(-x))*(-x+1))
}

der_dzeta_fn <- function(x) {
  fderiv(dzeta_fn,x,1)
}

rawratio <- function(res,x) {
  abs(2^(res+1i*x)*pi^(res+1i*x-1)*sin(pi/2*(res+1i*x))*gammaz(1-(res+1i*x)))
}
theta <- function(res,x) {
  sqrt(zeta(1-(res+1i*x))*rawratio(res,x)/zeta(res+1i*x))
}

x3 <- seq(0,199,l=19801);im_arg <- -0.00000000i
x4 <- floor(x3/2+0.5)

par(mfrow=c(1,1))

z1 <- function(z,im_arg) {
  ifelse(x3>1*z,1*Re(0+(zeta(1-1/z*(x3+im_arg))*abs(2^(1/z*(x3+im_arg))*
    pi^(1/z*(x3+im_arg)-1)*sin(pi/2*(1/z*(x3+im_arg)))*gammaz(1-1/z*(x3+im_arg))))),
    0)
}
z1_i <- function(z,im_arg) {
  ifelse(x3>1*z,1*Im(0+(zeta(1-1/z*(x3+im_arg))*abs(2^(1/z*(x3+im_arg))*
    pi^(1/z*(x3+im_arg)-1)*sin(pi/2*(1/z*(x3+im_arg)))*gammaz(1-1/z*(x3+im_arg))))),
    0)
}

z1_s <- function(z,im_arg) {
  ifelse(x3>2*z,2/2*Re(0+(zeta(1-1/z*(x3+im_arg))*abs(2^(1/z*(x3+im_arg))*
    pi^(1/z*(x3+im_arg)-1)*sin(pi/2*(1/z*(x3+im_arg)))*gammaz(1-1/z*(x3+im_arg))))),
    0)
}
z1_der <- function(x3) {
  fderiv(z1_s,x3,1)
}

z1log <- function(z,im_arg) {
  ifelse(x3>1*z,log(zeta(1-1/z*(x3+im_arg)))+log(abs(1/x3*2^(1/z*(x3+im_arg))*
    pi^(1/z*(x3+im_arg)-1)*sin(pi/2*(1/z*(x3+im_arg)))*gammaz(1-1/z*(x3+im_arg)))),
         0)
}

im_ar <- 0i

plot(x=(x3),y=(z1(1,im_ar)),typ="l",lwd=2,lty=2,xlim=c(0,30),ylim=c(-2,2),
     xlab="positive real axis",ylab="function value")
lines(x=(x3),y=(z1_i(1,im_ar)),col=2,lwd=2,lty=2)
# lines(x=(x3),y=(z1(3,im_ar)),col=2);lines(x=(x3),y=(z1(5,im_ar)),col=3);
# lines(x=(x3),y=(z1(7,im_ar)),col=4);lines(x=(x3),y=(z1(9,im_ar)),col=5);
# lines(x=(x3),y=(zeta(x3+1i*im_ar)),col=4)
# lines(x=(x3),y=z1_der(x3),col=5)
# lines(x=(x3),y=log(abs(z1_der(x3))),col=6)
lines(x=(x3),y=((zeta(x3))),col=4)
# lines(x=(x3),y=0.5*(1+z1(1,im_ar)),col=8)

legend(10, -1.2, c("Riemann Zeta fn", "Re(square wave Riemann Zeta generating fn)","Im(square wave Riemann Zeta generating fn)"),
       lty = 2,cex=.5, lwd = c(2,2,2), col = c("blue","black","red"))


```

***Fig.1:Riemann Zeta fn and a square wave Riemann Zeta generating fn on positive real axis.***

The identification of the positive odd integers occurs trivally because of the $sin(\frac{\pi s}{2})$ term but interestingly the product of $\zeta(1-s)$ and $abs(2^s\pi^{s-1}sin(\frac{\pi s}{2})\Gamma(1-s))$ plus $\zeta(s)$ rapidly tending to 1 produces the square wave behaviour.

This square wave behaviour allows the positive odd integers to be identified without recourse to arbitrarily defining a staircase function. That is, the function values for $\Re$ between the odd positive integers now have a piecewise continuous function defining their values.

This function when extended with a quotient argument s/n where n the denominator is the integer,

\begin{align}
\frac{Z_{ext}(\frac{s}{n})^2}{\zeta(\frac{s}{n})} = Z_{ext}(s)*e^{+i\theta_{ext}(s)} &= \zeta(1-\frac{s}{n})*abs(2^\frac{s}{n}\pi^{\frac{s}{n}-1}sin(\frac{\pi \frac{s}{n}}{2})\Gamma(1-\frac{s}{n})), \qquad \text{where } n \in \mathbb{N}  \label{eq:qsq}
\end{align}

can be used to test for prime numbers (inefficiently).


```{r, prime, echo=FALSE, cache=TRUE, fig.width=6, fig.height=5,  fig.keep='high', warning=FALSE }

plot(x=(x3),y=(z1_s(1,im_ar)),typ="l",lwd=2,lty=2,xlim=c(0,30),ylim=c(-2,2),
     xlab="positive real axis",ylab="function value")
lines(x=(x3),y=(z1_s(2,im_ar)),col=2)
lines(x=(x3),y=(z1_s(3,im_ar)),col=3)
lines(x=(x3),y=(z1_s(5,im_ar)),col=4)
lines(x=(x3),y=(z1_s(7,im_ar)),col=5)
# lines(x=(x3),y=(zeta(x3+1i*im_ar)),col=4)
# lines(x=(x3),y=z1_der(x3),col=5)
# lines(x=(x3),y=log(abs(z1_der(x3))),col=6)
# lines(x=(x3),y=0.5*(1+z1(1,im_ar)),col=8)

legend(26, 2, c("n=1","n=2","n=3","n=5","n=7"),
       lty = 2,cex=.5, lwd = c(2,2,2,2,2), col = c("black","red","green","blue","cyan"))


```

***Fig.2:Testing for prime numbers, dashed black lines without overlap of coloured lines are primes***

###Conclusions

The extended Riemann Siegel functions, can be used to define 

(i) the Riemann Zeta function as an interference pattern $\zeta(s) = Z_{ext}(s)*e^{-i\theta_{ext}(s)}$, 
(ii) the square wave Riemann Zeta function $Z_{ext}(s)*e^{+i\theta_{ext}(s)} = \zeta(1-s)*abs(2^s\pi^{s-1}sin(\frac{\pi s}{2})\Gamma(1-s))$ which identifies the positive odd integers and 
(iii) through quotient argument form (where the denominator n is integer) $\frac{Z_{ext}(\frac{s}{n})^2}{\zeta(\frac{s}{n})}=Z_{ext}(\frac{s}{n})*e^{+i\theta_{ext}(\frac{s}{n})}$ which identifies (inefficiently) prime numbers. 

This square wave function which allows input values (analytical continuation) off the positive real axis may give useful insights to the prime-counting function. 


###References

1. Edwards, H.M. (1974). Riemann's zeta function. Pure and Applied Mathematics 58. New York-London: Academic Press. ISBN 0-12-242750-0. Zbl 0315.10035.

2. Riemann, Bernhard (1859). "$\ddot{U}$ber die Anzahl der Primzahlen unter einer gegebenen Gr$\ddot{o}$sse". Monatsberichte der Berliner Akademie.. In Gesammelte Werke, Teubner, Leipzig (1892), Reprinted by Dover, New York (1953).

3. Berry, M. V. "The Riemann-Siegel Expansion for the Zeta Function: High Orders and Remainders." Proc. Roy. Soc. London A 450, 439-462, 1995.

4. Martin, J.P.D. "Applying the Argument Principle to the extended Riemann Siegel function components of the Riemann Zeta function" (2016)
http://dx.doi.org/10.6084/m9.figshare.4012290

