---
title: A Riemann Zeta magnitude growth function based on the Riemann Siegel Theta function closely mirrors the $|t^{-0.1548}\zeta(0.5+it)|$ behaviour for t < 10000.

author: "John Martin" 
date: "created:11/01/2018, last modified: 13/01/2018"
output:
  pdf_document:
    fig_crop: no
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Executive Summary

Using the continuous composite function $\theta(t)+e^{i\theta(t)}\zeta(0.5+it)$ and imposing the condition that $max(|\zeta_{norm}(0.5+it)|) = \pi(1+\gamma/2)$, a growth factor expression for $\zeta(0.5+it)$ can be derived, $\zeta_{growth factor}(0.5+it) =\frac{\pi(1+\frac{\gamma}{2})\frac{1}{\sqrt{\theta^{\prime}(t)^2+1}}+\theta(t+\pi(1+\frac{\gamma}{2}))\frac{\theta^{\prime}(t)}{\sqrt{\theta^{\prime}(t)^2+1}}-\theta(t)}{\pi(1+\frac{\gamma}{2})} 
\approx \frac{\theta(t+\pi(1+\frac{\gamma}{2}))-\theta(t)}{\pi(1+\frac{\gamma}{2})} = \theta^{\prime}(t) + \frac{\theta^{\prime\prime}(t)}{2}+...$. The growth factor closely mirrors, for low $t < 10000$ the current known Lindelof Hypothesis bound $t^{-0.1548}|\zeta(0.5+it)|$. The deviation for large t compared to $max(|\zeta_{norm}(0.5+it)|) = \pi(1+\gamma/2)$ for both growth estimates suggests extra functional dependence is required to improve both estimates or $max(|\zeta_{norm}(0.5+it)|) = \pi(1+\gamma/2) + f(t)$. 


```{r, exec_new, echo=FALSE, cache=TRUE, fig.width=7, fig.height=5,  fig.keep='high', warning=FALSE }

dir_loc <- "/home/john/bear/Projects/sampling-investigations/julia/"

read_fn <- function(dir_loc,filen){
  
  filenn <- paste0(dir_loc,filen)
  
  dread <- read.table(filenn,
                       sep=",", header=F,row.names=NULL)
}

res <- 0.5

df <- read_fn(dir_loc,"outfile_hurwitz_zeta_upper_with_xi_0_5.dat")

df[,"V1"] <- as.numeric(gsub("[^0-9\\.-]", "", df[,1]))
df[,"V2"] <- as.numeric(df[,2])
df[,"V3"] <- as.numeric(df[,3]) 
df[,"V4"] <- as.numeric(df[,4]) 
df[,"V5"] <- as.numeric(df[,5]) 
df[,"V6"] <- as.numeric(df[,6]) 
df[,"V7"] <- as.numeric(df[,7]) 
df[,"V8"] <- as.numeric(df[,8]) 
df[,"V9"] <- as.numeric(df[,9]) 
df[,"V10"] <- as.numeric(gsub("[^0-9\\.-]", "", df[,10]) )

df_l <- read_fn(dir_loc,"outfile_hurwitz_zeta_lower_with_xi_0_5.dat")

df_l[,"V1"] <- as.numeric(gsub("[^0-9\\.-]", "", df_l[,1]))
df_l[,"V2"] <- as.numeric(df_l[,2])
df_l[,"V3"] <- as.numeric(df_l[,3]) 
df_l[,"V4"] <- as.numeric(df_l[,4]) 
df_l[,"V5"] <- as.numeric(df_l[,5]) 
df_l[,"V6"] <- as.numeric(df_l[,6]) 
df_l[,"V7"] <- as.numeric(df_l[,7]) 
df_l[,"V8"] <- as.numeric(df_l[,8]) 
df_l[,"V9"] <- as.numeric(df_l[,9]) 
df_l[,"V10"] <- as.numeric(gsub("[^0-9\\.-]", "", df_l[,10]) )


reg_prop <- abs((df[,"V2"]+1i*df[,"V3"])/(df_l[,"V2"]+1i*df_l[,"V3"]))
theta <- sqrt((df[,"V2"]+1i*df[,"V3"])/(df_l[,"V2"]+1i*df_l[,"V3"])*reg_prop)
z <- sqrt((df[,"V2"]+1i*df[,"V3"])*(df_l[,"V2"]+1i*df_l[,"V3"])*reg_prop)


zet <- sqrt((df$V4+1i*df$V5)*(df_l$V4+1i*df_l$V5)*abs((df$V4+1i*df$V5)/(df_l$V4+1i*df_l$V5)))
the <- sqrt(1/(df$V4+1i*df$V5)*(df_l$V4+1i*df_l$V5)*abs((df$V4+1i*df$V5)/(df_l$V4+1i*df_l$V5)))

# x_series <- c(1:400000)



zet_2 <- sqrt((df$V6+1i*df$V7)*(df_l$V6+1i*df_l$V7)*abs((df$V6+1i*df$V7)/(df_l$V6+1i*df_l$V7)))
the_2 <- sqrt(1/(df$V6+1i*df$V7)*(df_l$V6+1i*df_l$V7)*abs((df$V6+1i*df$V7)/(df_l$V6+1i*df_l$V7)))

zet_3 <- sqrt((df$V8+1i*df$V9)*(df_l$V8+1i*df_l$V9)*abs((df$V8+1i*df$V9)/(df_l$V8+1i*df_l$V9)))
the_3 <- sqrt(1/(df$V8+1i*df$V9)*(df_l$V8+1i*df_l$V9)*abs((df$V8+1i*df$V9)/(df_l$V8+1i*df_l$V9)))

fu <- (-df$V1*log(2*pi/df$V1)/2-df$V1/2-pi/8+1/48/df$V1+7/5760/df$V1^3)#.02*df$V1^2+df$V1#
f1 <- (log(df$V1)/2-log(2*pi)/2-1*2/48/df$V1^2-7/5760*3/df$V1^4)#.04*df$V1^1+1*df$V1^0#
f2 <- 1/2/df$V1+3*2/48/df$V1^3#.04*df$V1^0#
ang_f1 <- atan(f1)
dx <- pi*(1+.57721/2)*cos(pi/2-ang_f1)
fu_shift <- (-(df$V1+abs(dx))*log(2*pi/(df$V1+abs(dx)))/2-(df$V1+abs(dx))/2-pi/8+1/48/(df$V1+abs(dx))+7/5760/(df$V1+abs(dx))^3)
dy1 <-  pi*(1+.57721/2)*sin(pi/2-ang_f1)

fdiff <- dy1+f1*abs(dx)+(dx)^2/2*f2
fdiff_shift <- dy1+fu_shift-fu
growth <- fdiff/(pi*(1+.57721/2))
growth_shift <- fdiff_shift/(pi*(1+.57721/2))

par(mfrow=c(1,2))
plot(x=df$V1,y=fu,col=3,typ="l",xlim=c(1960,1980),ylim=c(4645,4720),xlab="imag part",ylab="function value")
lines(x=df$V1,y=exp(1i*fu)*(df$V2+1i*df$V3)+fu,col=4,typ="l",xlim=c(0,40),ylim=c(0,100))
lines(x=df$V1,y=fu+fdiff,col=1,lty=3,typ="l",xlim=c(0,100),ylim=c(0,100))
lines(x=df$V1,y=fu-fdiff,col=1,lty=3,typ="l",xlim=c(0,100),ylim=c(0,100))
lines(x=df$V1,y=fu+fdiff_shift,col=2,lty=3,typ="l",xlim=c(0,100),ylim=c(0,100))
lines(x=df$V1,y=fu-fdiff_shift,col=2,lty=3,typ="l",xlim=c(0,100),ylim=c(0,100))
# lines(x=df$V1,y=fu+growth,col=2)
# lines(x=df$V1,y=fu+df$V1^(0.1548),col=5)
# lines(x=df$V1,y=fu+pi,col=7,lty=6)
abline(h=20,lty=3);abline(h=20+pi,lty=3);
legend("topleft", c("Theta(t)+Z(0.5+it)","Theta(t)", "upper peak bound","lower peak bound"),
       lty = c(1,1,3,3),cex=.8, lwd = c(2,2,2,2), col = c("blue","green","black","black"))


plot(x=df$V1,y=df$V1^(0.1548),typ="l",ylim=c(1,3.5),xlab="imag part",ylab="function value")
lines(x=df$V1,y=growth,col=3)
lines(x=df$V1,y=log(df$V1)/2-log(2*pi)/2,col=2)
lines(x=df$V1,y=abs(z)/abs((zet_3)),col=5)

legend("bottomright", c("|t^(-0.1548)zeta(0.5+it)|", "Theta(t) based \n zeta_growthfactor(0.5+it)","curve fitted growth factor","(log(t)-log(2pi))/2"),
       lty = c(1,1,1,1,2),cex=.7, lwd = c(2,2,2), col = c("black","green","cyan","red"))



```

***Behaviour of $\theta(t)+e^{i\theta(t)}\zeta(0.5+it)$ function highlighted by bounds on peak size and the current Lindelof Hypothesis bound $t^{-0.1548}$ and $\theta(t)$ based $\zeta_{growth factor}(0.5+it)$ magnitude for low t.***

##Introduction

On the critical line, in the limit $\Im(0.5+it) \rightarrow \infty$, the magnitude of the Riemann Zeta $\zeta(0.5+it) \rightarrow \infty$ (1-3). The Riemann Zeta function is defined (1), in the complex plane by the integral 

\begin{equation}
\zeta(s) = \frac{\prod(-s)}{2\pi i}\int_{C_{\epsilon,\delta}} \frac{(-x)^s}{(e^{x}-1)x}dx
\end{equation}


where $s \thinspace \epsilon \thinspace \mathbb{C}$ and $C_{\epsilon,\delta}$ is the contour about the imaginary poles.

The Riemann Zeta function has been shown to obey the functional equation (2)

\begin{equation}
\zeta(s) = 2^s\pi^{s-1}sin(\frac{\pi s}{2})\Gamma(1-s)\zeta(1-s) \label{eq:func}
\end{equation}

Following directly from the form of the functional equation and the properties of the coefficients on the RHS of eqn \eqref{eq:func} it has been shown that any zeroes off the critical line would be paired, ie. if $\zeta(s)$ = 0 was true then $\zeta(1-s) = 0$.

Along the critical line (0.5+it), the Riemann Siegel function is an exact function (3) for the magnitude of the Riemann Zeta function with two components Z(t) \& $\theta(t)$

\begin{equation}
Z(t) = \zeta(0.5+it)e^{i\theta(t)}  \label{eq:rs}
\end{equation}

and

\begin{align}
\theta(t) &= \Im(log(\Gamma(\frac{1}{4}+\frac{1}{2}it)))-\frac{t}{2}log(\pi) \nonumber \\
&= -\frac{t}{2}log(\frac{2\pi}{t})-\frac{t}{2}-\frac{\pi}{8}+\frac{1}{48t}+\frac{7}{7560t}+...\qquad \text{for } t \rightarrow \infty\label{eq:theta}
\end{align}

In Martin (4) the normalised Riemann Zeta function $\zeta_{norm}(s)$ within the critical strip was investigated using an exact curve fitted expression. This expression was shown numerically only to be valid for low $\Im(s)$, within the critical strip, however the following relationship and bounds were identified that could be applicable to all $\Im(s)$

\begin{align}
abs(\zeta_{norm}(s)) &\approx abs(\zeta_{norm}(1-s)) \label{eq:normfunc} \quad \text{for }0 \le \Re(s) \le 1 \text{, } \Im(s) > 2\pi
\end{align}


\begin{align}
max|\zeta_{norm}(s)| &= \pi(1+\frac{\gamma}{2}) \qquad \text{for } s=0.5+it \\
&\approx \pi \qquad \qquad \qquad \text{for } s=\pm1+it \label{eq:zetanormbdmax}
\end{align}

\begin{align}
min|\zeta_{norm}(s)| &\approx \frac{\gamma}{2} \qquad \qquad \text{for } s=\pm1+it \label{eq:zetanormbdmin}
\end{align}

Given the bounded nature of $\zeta_{norm}(s)$ for $\Im(s) > 2\pi$  and sharing the same non-trivial zeroes, the growth factor of the Reimann Zeta function magnitude, within the critical strip, can in principle be obtained as the ratio of the two functions

\begin{align}
\zeta_{growth factor}(s)&= \frac{maxbound|\zeta(s)|}{maxbound|\zeta_{norm}(s)|} \quad \text{for }0 \le \Re(s) \le 1 \label {eq:growth}
\end{align}

using curve fitting for low $\Im(s)$ (4), the growth factor estimate was 

\begin{equation}
\begin{split}
\zeta_{growth factor}(s) =abs\Big(e^{(-abs(\Re(s)-\frac{1}{2})+abs(\Im(s))\frac{\pi}{4}+\frac{\gamma}{4\pi})}\pi^{-\frac{s}{2}}\Gamma(\frac{s}{2})\Big) \quad \text{for }0 \le \Re(s) \le 1 \label {eq:growthseries}
\end{split}
\end{equation}

which had similar $\Im(s)$ behaviour to the current lowest bound $t^{-0.158}|\zeta(0.5+i\Im(s))|$ for the Lindelof hypothesis (5), for low $\Im(s)$ but eventually the $\zeta_{growth factor}(s)$ exhibited much higher estimates for growth at higher $\Im(s)$. That is, when comparing the calculated $max|\zeta_{norm}(s)|$ values at larger $\Im(s)$ for known large peaks (6)  $max(|\zeta_{norm}(s)|) \ll \pi, \Im(s) \rightarrow \infty$. Indeed, for very large $\Im(s)$ using data from (7), it is also the case that $t^{-0.158}|\zeta(0.5+i\Im(s))|$ exhibits diminishing values for large peaks as $\Im(s) \rightarrow \infty$.

In this paper, an alternate growth factor estimate based on the composite function $\theta(t)+\zeta(0.5+it)$ has been presented using eqn \eqref {eq:zetanormbdmax}, the previous observation that because the maximum peak height of $\zeta(0.5+it)$ tended to increase in increments of $\pi$ as $\Im(s)$ increased (8)

\begin{equation}
\Delta(max(\theta_{ext}(0.5+it)+|\zeta(0.5+it)|)-\theta_{ext}(0.5+it))) \approx \pi log(t)
\end{equation}

and a taylor series for the bounds of $\theta(t)+\zeta(0.5+it)$ .

##Deriving the $\theta(t)$ based growth factor on the critical line

As shown in (8), the imaginary logarithm of the Riemann Siegel Z function $\Im(log(Z_{ext}(s)))$ can be turned into a continuous function by careful mapping of the branch points which add $\pi$ around the position of each non-trivial zero. 
On the critical line, a similar function can easily be constructed by simply adding $\theta_{ext}(0.5+it)+|\zeta(0.5+it)|$ since $Z_{ext}(0.5+it)$ and $\theta_{ext}(0.5+it)+|\zeta(0.5+it)|$ share a $\theta_{ext}(0.5+it)$ dependence.

The other relevant idea from (8) is that the highest peaks of the Riemann Zeta function are bounded when expressed as $\theta_{ext}(0.5+it)+|\zeta(0.5+it)|$. 

Using calculations of the slope and normal of $\theta_{ext}(0.5+it)$ the upper and lower bounds of $\theta_{ext}(0.5+it)+|\zeta(0.5+it)|$ based on $\zeta_{norm}(0.5+it)$ are simply translated versions of $\theta_{ext}(0.5+it)$ separated by a constant distance of $\pi(1+\gamma/2)$ along the normal vector from $\theta_{ext}(0.5+it)$.

This means that vertical and horizontal displacement of the upper and lower bounds along the normal vector are  


\begin{align}
vertical displacement(\theta(t)+|\zeta(0.5+it)|)_{UB} = \Delta(y) &= \pi(1+\frac{\gamma}{2})sin(\frac{\pi}{2}-atan(\theta^{\prime}(t))) \\
vertical displacement(\theta(t)+|\zeta(0.5+it)|)_{LB} = -\Delta(y) &= -\pi(1+\frac{\gamma}{2})sin(\frac{\pi}{2}-atan(\theta^{\prime}(t)))
\end{align}

\begin{align}
horizontal displacement(\theta(t)+|\zeta(0.5+it)|)_{UB} = -\Delta(t) &= -\pi(1+\frac{\gamma}{2})cos(\frac{\pi}{2}-atan(\theta^{\prime}(t))) \\
horizontal displacement(\theta(t)+|\zeta(0.5+it)|)_{LB} = \Delta(t) &= +\pi(1+\frac{\gamma}{2})cos(\frac{\pi}{2}-atan(\theta^{\prime}(t)))
\end{align}

This mixed spacial displacement means that the function value of the upper and lower bounds vertically above any particular function point will be complex since $\theta(t)$ has curvature. 

Using, the known displacements and that the bound curves are parallel to $\theta(t)$ gives the formal functional behaviour 

\begin{align}
(\theta(t)+e^{i\theta(t)}\zeta(0.5+it))_{UB,LB} = \pm\Delta(y)+\theta(t\pm\Delta(t)) \label {eq:thetabds}
\end{align}

The growth factor is then derived from the ratio

\begin{align}
\zeta_{growth factor}(0.5+it) &= \frac{(\theta(t)+e^{i\theta(t)}\zeta(0.5+it))_{UB}-\theta(t)}{(\theta(t)+\pi(1+\frac{\gamma}{2}))-\theta(t)} \nonumber \\
&= \frac{(\theta(t)+e^{i\theta(t)}\zeta(0.5+it))_{UB}-\theta(t)}{\pi(1+\frac{\gamma}{2})} \label {eq:ratiodef}
\end{align}

using eqn \eqref {eq:thetabds} and geometrical relationships

\begin{align}
\zeta_{growth factor}(0.5+it) &= \frac{\Delta(y)+\theta(t+\Delta(t))-\theta(t)}{\pi(1+\frac{\gamma}{2})} \label {eq:ratiodef2} \\
&= \frac{\pi(1+\frac{\gamma}{2})sin(\frac{\pi}{2}-atan(\theta^{\prime}(t)))+\theta(t+\pi(1+\frac{\gamma}{2})cos(\frac{\pi}{2}-atan(\theta^{\prime}(t))))-\theta(t)}{\pi(1+\frac{\gamma}{2})} \\
&= \frac{\pi(1+\frac{\gamma}{2})cos(atan(\theta^{\prime}(t)))+\theta(t+\pi(1+\frac{\gamma}{2})sin(atan(\theta^{\prime}(t))))-\theta(t)}{\pi(1+\frac{\gamma}{2})} \\
&= \frac{\pi(1+\frac{\gamma}{2})\frac{1}{\sqrt{\theta^{\prime}(t)^2+1}}+\theta(t+\pi(1+\frac{\gamma}{2}))\frac{\theta^{\prime}(t)}{\sqrt{\theta^{\prime}(t)^2+1}}-\theta(t)}{\pi(1+\frac{\gamma}{2})} \label {eq:fullratio} \\
&\approx \frac{\theta(t+\pi(1+\frac{\gamma}{2}))-\theta(t)}{\pi(1+\frac{\gamma}{2})} = \theta^{\prime}(t) \qquad \text{for } t \rightarrow \infty
\end{align}


The ratio can also be expressed using second order taylor series to reveal additional series terms for low t

\begin{align}
(\theta(t)+|\zeta(0.5+it)|)_{UB,LB} &= \theta(t)\pm\pi*(1+\frac{\gamma}{2})\Big(\theta^{\prime}(t)cos(\frac{\pi}{2}-atan(\theta^{\prime}(t)))+... \nonumber \\ &+\frac{\theta^{\prime\prime}(t)}{2}cos(\frac{\pi}{2}-atan(\theta^{\prime}(t)))^2+sin(\frac{\pi}{2}-atan(\theta^{\prime}(t)))\Big) \\
&\approx\theta(t)\pm\pi*(1+\frac{\gamma}{2})\Big(\theta^{\prime}(t)sin(atan(\theta^{\prime}(t)))+\frac{\theta^{\prime\prime}(t)}{2}sin(atan(\theta^{\prime}(t)))^2+cos(atan(\theta^{\prime}(t)))\Big) \\
&\approx\theta(t)\pm\pi*(1+\frac{\gamma}{2})\Big(\theta^{\prime}(t)\frac{\theta^{\prime}(t)}{\sqrt{\theta^{\prime}(t)^2+1}}+\frac{\theta^{\prime\prime}(t)}{2}(\frac{\theta^{\prime}(t)}{\sqrt{\theta^{\prime}(t)^2+1}})^2+\frac{1}{\sqrt{\theta^{\prime}(t)^2+1}}\Big) \\
&\approx\theta(t)\pm\pi*(1+\frac{\gamma}{2})\Big(\theta^{\prime}(t)+\frac{\theta^{\prime\prime}(t)}{2}+...\Big)\end{align}

The resultant growth factor is then the ratio estimate

\begin{align}
\zeta_{growth factor}(0.5+it) &= \frac{\big((\theta(t)+|\zeta(0.5+it)|)_{UB}-\theta(t)\big)}{max|\zeta_{norm}(0.5+it)|} \nonumber \\ &\approx\theta^{\prime}(t)+\frac{\theta^{\prime\prime}(t)}{2}+... \label {eq:tsgrowth}
\end{align}

It is also noted that $\theta(t)$ is very suitable for second order taylor series expansion away from real axis given

\begin{align}
\theta(t) &= -\frac{t}{2}log(\frac{2\pi}{t})-\frac{t}{2}-\frac{\pi}{8}+\frac{1}{48t}+\frac{7}{7560t}+...\qquad \text{for } t \rightarrow \infty\label{eq:thetafn}
\end{align}

\begin{align}
\theta^{\prime}(t) &= \frac{log(t)}{2}-\frac{log(2\pi)}{2}+... \qquad \text{for } t \rightarrow \infty\label{eq:thetaprime}
\end{align}

\begin{align}
\theta^{\prime\prime}(t) &= \frac{1}{2t}+... \qquad \text{for } t \rightarrow \infty\label{eq:thetaprime2}
\end{align}

Collecting the leading terms 
\begin{align}
\zeta_{growth factor}(0.5+it) &\approx \frac{(log(t)-log(2\pi))}{2} +\frac{1}{4t}+... \label {eq:tsgrowth}
\end{align}

##Results

The following two graphs plus the executive summary graph show the close correspondence of the $\theta(t)$ growth factor of the Riemann Zeta magnitude along the critical line to the current Lindelof Hypothesis bound $t^{-0.1548}|\zeta(0.5+it)|$ for low t and the curved fitted growth factor from (4)

Comparing the three figures, 

(i) the change of frame of reference from the unscaled presentation of  $|\zeta(0.5+it)|$ to the scaled sloping function $\theta(t)+e^{i\theta(t)}\zeta(0.5+it)$ with integral scaling by $\pi$ allows the highest peaks of the Riemann Zeta function to be recognised as bounded features. The gradual growth of large peaks by $\pi$ can now be understood arising from $\theta(t)$ influencing the bounds of the function amplitude as well as the periodicity of the zeroes. 

(ii) the $\theta(t)+e^{i\theta(t)}\zeta(0.5+it)$ based growth factor is closer to the Lindelof Hypothesis upper bound result than the curve fitted growth factor from (4) reflecting the deeper concept that $\theta(t)+e^{i\theta(t)}\zeta(0.5+it)$ represents compared to curve fitting at low t

(iii) the executive summary figure, in particular shows that the $\theta(t)+e^{i\theta(t)}\zeta(0.5+it)$ growth factor is actually very similar to the Lindelof Hypothesis upper bound and may represent a natural limiting value for the t^{-0.1458} estimate methodology.


```{r, fig_1, echo=FALSE, cache=TRUE, fig.width=7, fig.height=5,  fig.keep='high', warning=FALSE }

dir_loc <- "/home/john/bear/Projects/sampling-investigations/julia/"

read_fn <- function(dir_loc,filen){
  
  filenn <- paste0(dir_loc,filen)
  
  dread <- read.table(filenn,
                       sep=",", header=F,row.names=NULL)
}

res <- 0.5

df <- read_fn(dir_loc,"outfile_hurwitz_zeta_upper_with_xi_0_5.dat")

df[,"V1"] <- as.numeric(gsub("[^0-9\\.-]", "", df[,1]))
df[,"V2"] <- as.numeric(df[,2])
df[,"V3"] <- as.numeric(df[,3]) 
df[,"V4"] <- as.numeric(df[,4]) 
df[,"V5"] <- as.numeric(df[,5]) 
df[,"V6"] <- as.numeric(df[,6]) 
df[,"V7"] <- as.numeric(df[,7]) 
df[,"V8"] <- as.numeric(df[,8]) 
df[,"V9"] <- as.numeric(df[,9]) 
df[,"V10"] <- as.numeric(gsub("[^0-9\\.-]", "", df[,10]) )

df_l <- read_fn(dir_loc,"outfile_hurwitz_zeta_lower_with_xi_0_5.dat")

df_l[,"V1"] <- as.numeric(gsub("[^0-9\\.-]", "", df_l[,1]))
df_l[,"V2"] <- as.numeric(df_l[,2])
df_l[,"V3"] <- as.numeric(df_l[,3]) 
df_l[,"V4"] <- as.numeric(df_l[,4]) 
df_l[,"V5"] <- as.numeric(df_l[,5]) 
df_l[,"V6"] <- as.numeric(df_l[,6]) 
df_l[,"V7"] <- as.numeric(df_l[,7]) 
df_l[,"V8"] <- as.numeric(df_l[,8]) 
df_l[,"V9"] <- as.numeric(df_l[,9]) 
df_l[,"V10"] <- as.numeric(gsub("[^0-9\\.-]", "", df_l[,10]) )


reg_prop <- abs((df[,"V2"]+1i*df[,"V3"])/(df_l[,"V2"]+1i*df_l[,"V3"]))
theta <- sqrt((df[,"V2"]+1i*df[,"V3"])/(df_l[,"V2"]+1i*df_l[,"V3"])*reg_prop)
z <- sqrt((df[,"V2"]+1i*df[,"V3"])*(df_l[,"V2"]+1i*df_l[,"V3"])*reg_prop)


zet <- sqrt((df$V4+1i*df$V5)*(df_l$V4+1i*df_l$V5)*abs((df$V4+1i*df$V5)/(df_l$V4+1i*df_l$V5)))
the <- sqrt(1/(df$V4+1i*df$V5)*(df_l$V4+1i*df_l$V5)*abs((df$V4+1i*df$V5)/(df_l$V4+1i*df_l$V5)))

x_series <- c(1:400000)



zet_2 <- sqrt((df$V6+1i*df$V7)*(df_l$V6+1i*df_l$V7)*abs((df$V6+1i*df$V7)/(df_l$V6+1i*df_l$V7)))
the_2 <- sqrt(1/(df$V6+1i*df$V7)*(df_l$V6+1i*df_l$V7)*abs((df$V6+1i*df$V7)/(df_l$V6+1i*df_l$V7)))

zet_3 <- sqrt((df$V8+1i*df$V9)*(df_l$V8+1i*df_l$V9)*abs((df$V8+1i*df$V9)/(df_l$V8+1i*df_l$V9)))
the_3 <- sqrt(1/(df$V8+1i*df$V9)*(df_l$V8+1i*df_l$V9)*abs((df$V8+1i*df$V9)/(df_l$V8+1i*df_l$V9)))

fu <- (-df$V1*log(2*pi/df$V1)/2-df$V1/2-pi/8+1/48/df$V1+7/5760/df$V1^3)#.02*df$V1^2+df$V1#
f1 <- (log(df$V1)/2-log(2*pi)/2-1*2/48/df$V1^2-7/5760*3/df$V1^4)#.04*df$V1^1+1*df$V1^0#
f2 <- 1/2/df$V1+3*2/48/df$V1^3#.04*df$V1^0#
ang_f1 <- atan(f1)
dx <- pi*(1+.57721/2)*cos(pi/2-ang_f1)
dy1 <-  pi*(1+.57721/2)*sin(pi/2-ang_f1)

fdiff <- dy1+f1*abs(dx)+(dx)^2/2*f2
growth <- fdiff/(pi*(1+.57721/2))

par(mfrow=c(1,2))
plot(x=df$V1,y=fu,col=3,typ="l",xlim=c(0,50),ylim=c(0,50),xlab="imag part",ylab="function value")
lines(x=df$V1,y=exp(1i*fu)*(df$V2+1i*df$V3)+fu,col=4,typ="l")
lines(x=df$V1,y=fu+fdiff,col=1,lty=3,typ="l")
lines(x=df$V1,y=fu-fdiff,col=1,lty=3,typ="l")
legend("topleft", c("Theta(t)+Z(0.5+it)","Theta(t)", "upper peak bound","lower peak bound"),
       lty = c(1,1,3,3),cex=.8, lwd = c(2,2,2,2), col = c("blue","green","black","black"))


plot(x=df$V1,y=df$V1^(0.1548),typ="l",xlim=c(0,50),ylim=c(1,3.5),xlab="imag part",ylab="function value")
lines(x=df$V1,y=growth,col=3)
lines(x=df$V1[x_series],y=abs(z)[x_series]/abs((zet_3[x_series])),col=5)

legend("topright", c("|t^(-0.1548)zeta(0.5+it)|", "Theta(t) based \n zeta_growthfactor(0.5+it)","curve fitted growth factor"),
       lty = c(1,1,1),cex=.8, lwd = c(2,2,2), col = c("black","green","cyan"))



```

***Behaviour of $\theta(t)+e^{i\theta(t)}\zeta(0.5+it)$ function for very low t, highlighted by bounds on peak size and the current Lindelof Hypothesis bound $t^{-0.1548}$, $\theta(t)$ based $\zeta_{growth factor}(0.5+it)$ magnitude for low t and a curve fitted growth factor.***


```{r, fig_2, echo=FALSE, cache=TRUE, fig.width=7, fig.height=5,  fig.keep='high', warning=FALSE }

dir_loc <- "/home/john/bear/Projects/sampling-investigations/julia/"

read_fn <- function(dir_loc,filen){
  
  filenn <- paste0(dir_loc,filen)
  
  dread <- read.table(filenn,
                       sep=",", header=F,row.names=NULL)
}

res <- 0.5

df <- read_fn(dir_loc,"outfile_hurwitz_zeta_upper_with_xi_0_5.dat")

df[,"V1"] <- as.numeric(gsub("[^0-9\\.-]", "", df[,1]))
df[,"V2"] <- as.numeric(df[,2])
df[,"V3"] <- as.numeric(df[,3]) 
df[,"V4"] <- as.numeric(df[,4]) 
df[,"V5"] <- as.numeric(df[,5]) 
df[,"V6"] <- as.numeric(df[,6]) 
df[,"V7"] <- as.numeric(df[,7]) 
df[,"V8"] <- as.numeric(df[,8]) 
df[,"V9"] <- as.numeric(df[,9]) 
df[,"V10"] <- as.numeric(gsub("[^0-9\\.-]", "", df[,10]) )

df_l <- read_fn(dir_loc,"outfile_hurwitz_zeta_lower_with_xi_0_5.dat")

df_l[,"V1"] <- as.numeric(gsub("[^0-9\\.-]", "", df_l[,1]))
df_l[,"V2"] <- as.numeric(df_l[,2])
df_l[,"V3"] <- as.numeric(df_l[,3]) 
df_l[,"V4"] <- as.numeric(df_l[,4]) 
df_l[,"V5"] <- as.numeric(df_l[,5]) 
df_l[,"V6"] <- as.numeric(df_l[,6]) 
df_l[,"V7"] <- as.numeric(df_l[,7]) 
df_l[,"V8"] <- as.numeric(df_l[,8]) 
df_l[,"V9"] <- as.numeric(df_l[,9]) 
df_l[,"V10"] <- as.numeric(gsub("[^0-9\\.-]", "", df_l[,10]) )


reg_prop <- abs((df[,"V2"]+1i*df[,"V3"])/(df_l[,"V2"]+1i*df_l[,"V3"]))
theta <- sqrt((df[,"V2"]+1i*df[,"V3"])/(df_l[,"V2"]+1i*df_l[,"V3"])*reg_prop)
z <- sqrt((df[,"V2"]+1i*df[,"V3"])*(df_l[,"V2"]+1i*df_l[,"V3"])*reg_prop)


zet <- sqrt((df$V4+1i*df$V5)*(df_l$V4+1i*df_l$V5)*abs((df$V4+1i*df$V5)/(df_l$V4+1i*df_l$V5)))
the <- sqrt(1/(df$V4+1i*df$V5)*(df_l$V4+1i*df_l$V5)*abs((df$V4+1i*df$V5)/(df_l$V4+1i*df_l$V5)))

x_series <- c(1:400000)



zet_2 <- sqrt((df$V6+1i*df$V7)*(df_l$V6+1i*df_l$V7)*abs((df$V6+1i*df$V7)/(df_l$V6+1i*df_l$V7)))
the_2 <- sqrt(1/(df$V6+1i*df$V7)*(df_l$V6+1i*df_l$V7)*abs((df$V6+1i*df$V7)/(df_l$V6+1i*df_l$V7)))

zet_3 <- sqrt((df$V8+1i*df$V9)*(df_l$V8+1i*df_l$V9)*abs((df$V8+1i*df$V9)/(df_l$V8+1i*df_l$V9)))
the_3 <- sqrt(1/(df$V8+1i*df$V9)*(df_l$V8+1i*df_l$V9)*abs((df$V8+1i*df$V9)/(df_l$V8+1i*df_l$V9)))

fu <- (-df$V1*log(2*pi/df$V1)/2-df$V1/2-pi/8+1/48/df$V1+7/5760/df$V1^3)#.02*df$V1^2+df$V1#
f1 <- (log(df$V1)/2-log(2*pi)/2-1*2/48/df$V1^2-7/5760*3/df$V1^4)#.04*df$V1^1+1*df$V1^0#
f2 <- 1/2/df$V1+3*2/48/df$V1^3#.04*df$V1^0#
ang_f1 <- atan(f1)
dx <- pi*(1+.57721/2)*cos(pi/2-ang_f1)
dy1 <-  pi*(1+.57721/2)*sin(pi/2-ang_f1)

fdiff <- dy1+f1*abs(dx)+(dx)^2/2*f2
growth <- fdiff/(pi*(1+.57721/2))

par(mfrow=c(1,2))
plot(x=df$V1,y=fu,col=3,typ="l",xlim=c(270,300),ylim=c(360,440),xlab="imag part",ylab="function value")
lines(x=df$V1,y=exp(1i*fu)*(df$V2+1i*df$V3)+fu,col=4,typ="l")
lines(x=df$V1,y=fu+fdiff,col=1,lty=3,typ="l")
lines(x=df$V1,y=fu-fdiff,col=1,lty=3,typ="l")
legend("topleft", c("Theta(t)+Z(0.5+it)","Theta(t)", "upper peak bound","lower peak bound"),
       lty = c(1,1,3,3),cex=.8, lwd = c(2,2,2,2), col = c("blue","green","black","black"))


plot(x=df$V1,y=df$V1^(0.1548),typ="l",xlim=c(270,300),ylim=c(1,3.5),xlab="imag part",ylab="function value")
lines(x=df$V1,y=growth,col=3)
lines(x=df$V1[x_series],y=abs(z)[x_series]/abs((zet_3[x_series])),col=5)

legend("topright", c("|t^(-0.1548)zeta(0.5+it)|", "Theta(t) based \n zeta_growthfactor(0.5+it)","curve fitted growth factor"),
       lty = c(1,1,1),cex=.8, lwd = c(2,2,2), col = c("black","green","cyan"))



```

***Behaviour of $\theta(t)+e^{i\theta(t)}\zeta(0.5+it)$ function for slightly higher t, highlighted by bounds on peak size and the current Lindelof Hypothesis bound $t^{-0.1548}$, $\theta(t)$ based $\zeta_{growth factor}(0.5+it)$ magnitude for low t and a curve fitted growth factor.***


##High t issues for growth factor estimates, to be continued

Using known lists of $\zeta(s)$ maxima (5,7) for higher t the three growth factors $|t^{-0.1548}\zeta(s)|$, $\zeta_{growth factor}(0.5+it)$ and curve fitted factor (4) all fail to be consistent with the idea of a flat bound in magnitude for $\zeta_{norm}(s)$ of $\pi(1+\gamma/2)$ on the critical line. 

In the results below, if the calculated peak heights represent growth from a baseline normalised Riemann Zeta function, then scaled values of $\sim \pi(1+\gamma/2) \approx 4.048$ would have been expected for $\zeta_{norm}(s)$ & $|t^{-0.1548}\zeta(s)|$


for s=1/2+1i*2445745756408.35596, 
$\zeta(s)$ = 297.435, $\zeta_{norm}(s)$ = 22.22, $|t^{-0.1548}\zeta(s)|$ = 3.60

for s=1/2+1i*310678833629083965667540576593682.058,
$\zeta(s)$ = 16858.119, $\zeta_{norm}(s)$ = 461.8294, $|t^{-0.1548}\zeta(s)|$ = 0.157398

The following two graphs show the low t behaviour and the high t behaviour of $t^{0.1548}$ and $\theta(t)$ based $\zeta_{growth factor}(0.5+it)$ plus some known large Riemann Zeta peaks (scaled by $\pi(1+\gamma/2)$) to represent empirical growth factors if $max(|\zeta_{norm}(0.5+it)|) = \pi(1+\gamma/2)$ is assumed to be true for all t .

```{r, fig_3, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4,  fig.keep='high', warning=FALSE }


fug <- function(g) {(-g*log(2*pi/g)/2-g/2-pi/8+1/48/g+7/5760/g)}
f1g <- function(g) {(log(g)/2-log(2*pi)/2-1*2/48/g^2-7/5760*3/g^4)}
f2g <- function(g) {1/2/g+3*2/48/g^3}

xs <- (seq(1,5,l=201))
plot(x=(10^xs),y=log((10^xs)^0.1548*pi*(1+.57721/2)),typ="l",col=4,
     ylab="log(function value)",xlab="imag part")
lines(x=(10^xs),y=log(f1g(10^xs)*pi*(1+.57721/2)),col=3)
legend("bottomright", c("t^(0.1548)","Theta(t) based growth"),
       lty = c(1,1),cex=.8, lwd = c(2,2), col = c("blue","green"))


```

***low t Behaviour of growth factor estimates.***



```{r, fig_4, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4,  fig.keep='high', warning=FALSE }


fug <- function(g) {(-g*log(2*pi/g)/2-g/2-pi/8+1/48/g+7/5760/g)}
f1g <- function(g) {(log(g)/2-log(2*pi)/2-1*2/48/g^2-7/5760*3/g^4)}
f2g <- function(g) {1/2/g+3*2/48/g^3}

scaled_peaks_x <- c(310678833629083965667540576593682.058,5032868769288289111.35,70391066310491324308791969554453.2490,552166410009931288886808632346.5052,35575860004214706249227248805977.2412,725177880629981.914,5032868769288289111.35,803625728592344363123814218778.1993,363991205.17884,3443895116.94519,31051083602.36298,153603679979.85403,258067466059.90668,295126484043.95032,326473979757.42792,875657660079.99756,906557871638.31824,1720474107149.35352,2371699985550.72070,690422639823936254540302269442.4854,6436526919750171929565.992,73027109216315547125974615.940)
scaled_peaks_h <- c(16858.119,1581.7,14055.8928,13558.8331,13338.6875,453.9,1581.7,10282.6496,114.446,152.391,213.895,241.259,262.207,267.090,289.782,306.450,324.941,331.596,339.720,10268.7134,2942.71,5297.23)/pi/(1+.57721/2)

xs <- (seq(1,32,l=2001))
plot(x=log(10^xs),y=log((10^xs)^0.1548*pi*(1+.57721/2)),typ="l",col=4,
     ylab="log(function value)",xlab="log(imag part)")
lines(x=log(10^xs),y=log(f1g(10^xs)*pi*(1+.57721/2)),col=3)
points(x=log(scaled_peaks_x),y=log(scaled_peaks_h),pch=4,col=2)
legend("topleft", c("t^(0.1548)","Theta(t) based growth","scaled known zeta peaks"),
       lty = c(1,1,1),cex=.8, lwd = c(2,2,2), col = c("blue","green","red"),pch=c(1,1,4))




```

***high t Behaviour of growth factor estimates and some scaled known peaks***


###Conclusions

The composite function $\theta(t)+e^{i\theta(t)}\zeta(0.5+it)$ in tandem with the concept of a flat bounded normalised Riemann Zeta function can be used to derive a growth factor estimate for the magnitude of the Riemann Zeta function, valid for low $\Im(s)$. The approach also has a useful frame of reference change to understand the rate of change in the highest peaks. 

Comparing to calculations using the latest known Lindelof Hypothesis bound results $t^{-0.158}|\zeta(0.5+it)|$, a fully consistent $\zeta_{norm}(s)$ functional form for all large $\Im(s)$ within the critical strip, requires additonal functional dependence in all these growth factor estimates or the assumption of $max(|\zeta_{norm}(0.5+it)|) = \pi(1+\gamma/2)$ is failing. 


###References

1. Edwards, H.M. (1974). Riemann's zeta function. Pure and Applied Mathematics 58. New York-London: Academic Press. ISBN 0-12-242750-0. Zbl 0315.10035.

2. Riemann, Bernhard (1859). "$\ddot{U}$ber die Anzahl der Primzahlen unter einer gegebenen Gr$\ddot{o}$sse". Monatsberichte der Berliner Akademie.. In Gesammelte Werke, Teubner, Leipzig (1892), Reprinted by Dover, New York (1953).

3. Berry, M. V. "The Riemann-Siegel Expansion for the Zeta Function: High Orders and Remainders." Proc. Roy. Soc. London A 450, 439-462, 1995.

4. Martin, J.P.D. "Exact functional dependence for the growth in the magnitude of the Riemann Zeta function within the critical strip" (2018)
http://dx.doi.org/10.6084/m9.figshare.5765796

5. numbers.computation.free.fr/Constants/Miscellaneous/MaxiZAll.txt
Copyright © 1999-2010 by Xavier Gourdon & Pascal Sebah

6. Bourgain, Jean (2017), "Decoupling, exponential sums and the Riemann zeta function", Journal of the American Mathematical Society, 30 (1): 205–224, arXiv:1408.5794 doi:10.1090/jams/860

7. Tihanyi, N., Kovács, A. & Kovács, J. "Computing Extremely Large Values of the Riemann Zeta Function" J Grid Computing (2017) 15: 527. https://doi.org/10.1007/s10723-017-9416-0

8. Martin, J.P.D. "Mapping the Extended Riemann Siegel Z Theta Functions about branch points in the complex plane" (2016)
http://dx.doi.org/10.6084/m9.figshare.3813999

